### 2020-04-29 final_report/methodology.tex
even better figures, more comments from Nikos implemented
implement more Vignesh comments

	\caption{Selected parametric neural network architectures. All layers except
		the last use ReLU activation. Prediction information flow is indicated by
		arrows. Connections between neurons are omitted for clarity.}
	\label{fig:nn-archs}
\end{figure}

@@

The aim of the initial experiments is to use a relatively small subset of
collected TBR samples to determine hyperparameters of considered surrogates.
Since this process requires learning the behaviour of an unknown, possibly
expensive mapping---here a function that assigns cross-validated metrics to a
point in the hyperparameter domain---it in many aspects mirrors
the primary task of this work with the notable extension of added utility
to optimise. In order to avoid undesirable exponential slowdown in exhaustive
searches of a possibly high-dimensional parameter space, Bayesian
optimisation is employed as a standard hyperparameter tuning algorithm. We set
its objective to maximise $R^2$ and perform 1000~iterations.\footnote{Tuning of
	each surrogate class was artificially terminated after 2~days. Instances
	which reached this limit are marked in the results.}

% TODO: mark instances that timed out in results

In the first experiment, efforts are made to maximise the possibility of success
in surrogates that are prone to suboptimal performance in discontinuous spaces.
This follows the notion that, if desired, accuracy of such models may be
replicated at large scale by decomposing the TBR domain into continuous subsets,
and learning ensemble surrogate comprised of identical models that are trained on each
subset independently, incurring exponential complexity penalty in the process.
To this end, data are limited to a single slice from run~2, and discrete
features are completely withheld from evaluated
surrogates. This is repeated for each of the four available slices to
investigate variance in behaviour under different discrete feature assignments.

>>>>

	\caption{Selected parametric neural network architectures. All layers except
		the last use ReLU activation. Prediction information flow is indicated by
		arrows.}
	\label{fig:nn-archs}
\end{figure}

@@

The aim of the initial experiments is to use a relatively small subset of
collected TBR samples to determine hyperparameters of considered surrogates.
Since this process requires learning the behaviour of an unknown, possibly
expensive mapping---here a function that assigns cross-validated metrics to a
point in the hyperparameter domain---it in many aspects mirrors
the primary task of this work with the notable extension of added utility
to optimise. In order to avoid undesirable exponential slowdown in exhaustive
searches of a possibly high-dimensional parameter space, Bayesian
optimisation is employed as a standard hyperparameter tuning algorithm. We set
its objective to maximise $R^2$ and perform
1000~iterations.\footnote{Hyperparameter tuning of each surrogate family was
	terminated after 2~days. Instances that reached this limit may be identified
	in~\cref{tbl:exp1-detailed-results,tbl:exp2-detailed-results}.}

In the first experiment, efforts are made to maximise the possibility of success
in surrogates that are prone to suboptimal performance in discontinuous spaces.
This follows the notion that, if desired, accuracy of such models may be
replicated by training separate instances to model each continuous subregion of
the domain independently.
To this end, data are limited to a single slice from run~2, and discrete
features are completely withheld from evaluated
surrogates. This is repeated for each of the four available slices to
investigate variance in behaviour under different discrete feature assignments.
